Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Compare to other works

\newcommand{\christine}[1]{{\color{green} Christine:#1}}

@@

In \cref{existing}, we review existing approaches for solving the MCS problem, with a specific focus
on Constraint Programming (CP)-based approaches, and on approaches that reduce the problem to
finding a maximum clique in an association graph.

Conventional wisdom is that clique-based approaches are less effective in practice, but previous
experimental evaluations have used weak clique algorithms, or even maximal clique enumeration
algorithms.  Therefore, in \cref{eval1}, we  re-evaluate the clique-based approach using a modern
algorithm, and we show that it outperforms CP on labelled graphs, and that it is competitive with CP
on unlabelled graphs.

@@

\christine{The approach should be compared with the approach proposed in \cite{DBLP:conf/mco/VismaraV08}.}

@@

In \cref{algorithm:mccis} we present a clique-inspired algorithm which finds a maximum common
connected induced subgraph isomorphism via an association graph. If the additional branching
restrictions are removed, the core of the algorithm is the same as the ``MCSa1'' clique algorithm
used in the previous section (and we refer the reader to the previously cited works for
implementation details on how to use bitsets and other data structures to implement the colouring
stage with very low constant factors).

>>>>

@@

In \cref{existing}, we review existing approaches for solving the MCS problem, with a specific focus
on Constraint Programming (CP)-based techniques, and on reductions of the problem to finding a
maximum clique in an association graph.

Previous experimental evaluations have used weak maximum clique algorithms, or even enumeration
algorithms---for example, Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} compare a modified form
of the Bron-Kerbosch maximal clique enumeration algorithm \cite{Bron:1973:AFC:362342.362367} with a
CP optimisation approach. Our experience suggests that the optimisation form of the clique problem
is often many orders of magnitude easier than enumeration, due to the possibility of employing a
strong bound function to prune the search space.  Therefore, in \cref{eval1}, we  re-evaluate the
clique-based approach using a modern algorithm, and we show that it outperforms CP on labelled
graphs, and that it is competitive with CP on unlabelled graphs.

@@

@@

In \cref{algorithm:mccis} we present a clique-inspired algorithm which finds a maximum common
connected induced subgraph isomorphism via an association graph. If the additional branching
restrictions are removed, the core of the algorithm is the same as the ``MCSa1'' clique algorithm
used in the previous section (and we refer the reader to the previously cited works for
implementation details on how to use bitsets and other data structures to implement the colouring
stage with very low constant factors). The approach we describe here differs considerably from that
of Koch \cite{DBLP:journals/tcs/Koch01} and Vismara and Valery \cite{DBLP:conf/mco/VismaraV08}:
these earlier approaches worked by classifying labels in the association graph based upon whether a
common vertex is shared, and then constructing cliques with particular edge properties---this is
harder to integrate with a strong bound function.
